preciseTAD: A machine learning framework for precise TAD boundary prediction at base-level resolution

### 2020-08-30 Manuscript/manuscript.Rmd
Add new writeup about Supp Fig 5CD

Next, we evaluated the biological significance of *preciseTAD* boundaries. Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, co-localized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead called TAD and Peakached loop boundaries respectively (Figure 5B-5C; Supplementary Figure 5). Furthermore, signal heatmaps indicated that our predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7). *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Supplementary Figure 8). These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.

>>>>

Next, we evaluated the biological significance of *preciseTAD* boundaries. Peak regions associated with known molecular drivers of 3D chromatin, including CTCF, RAD21, SMC3, and ZNF143, co-localized more frequently around *preciseTAD*-predicted TAD and loop boundaries compared to Arrowhead called TAD and Peakachu loop boundaries respectively (Figure 5B, C; Supplementary Figure 5A, B). Surprised by the poor signal distribution at the Arrowhead boundaries, we compared signals centered on boundaries called by Arrowhead, Peakachu, and our SpectralTAD [@Cresswell:2020ab] TAD caller. We confirmed the poor signal distribution around Arrowhead boundaries, in contrast to the well-performing Peakachu- and SpectralTAD-called boundaries (Supplementary Figure 5C, D). Furthermore, signal heatmaps indicated that *preciseTAD*-predicted boundaries were more enriched for the same genomic annotations than either Arrowhead or Peakachu boundaries alone (Supplementary Figures 6-7). *preciseTAD* boundaries were statistically significantly closer to the top-ranked TFBS (Wilcoxon p-value < 0.001 versus Arrowhead and Peakachu boundaries, respectively, Figure 6A, Supplementary Figure 8). These results indicate that *preciseTAD*-predicted boundaries better reflected the known biology of boundary formation.
